### 2022-12-28 Manuscript/Draft1.Rmd
attemps at citations

---
csl: canadian-journal-of-fisheries-and-aquatic-sciences.csl
output:
  bookdown::pdf_document2:
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: yes
  bibliography: IBMWG.bib

>>>>

---
csl: canadian-journal-of-fisheries-and-aquatic-sciences.csl
output:
  bookdown::pdf_document2:
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: yes
  citation_package: biblatex
  bibliography: IBMWG.bib
